\documentclass[letterpaper, 10pt]{article}
\usepackage{graphicx} % Required for inserting images
\usepackage[hidelinks]{hyperref} % Required for hyperlinks
\usepackage[top=0.5in, bottom=0.5in, left=0.7in, right=0.7in]{geometry} % Page margins
\pagestyle{empty} % No page numbers

\begin{document}

%----------HEADING-------------------------------------------------------------
\begin{center}
    \textbf{\LARGE Hojeong Ryu} \\ \vspace{2pt}
    \href{mailto:ifnjtqifsf@skku.edu}{\underline{ifnjtqifsf@skku.edu}} $|$ 
    \href{https://github.com/zldrkt}{\underline{github.com/zldrkt}}
\end{center}

%----------TECHNICAL SKILLS----------------------------------------------------
\section*{Technical Skills}
\hrule
\vspace{4pt}
\begin{itemize}
    \item[] \textbf{Programming}: C, C++, Python
    \item[] \textbf{Frameworks \& Tools}: Markdown, LaTeX, Git, Docker, VS Code
    \item[] \textbf{Languages}: English
\end{itemize}

%----------EXPERIENCE----------------------------------------------------------
\section*{Experience}
\hrule
\vspace{4pt}
\begin{itemize}
    \item 
    \textbf{Algorithm Problem Solving Study} \hfill Mar. 2026 -- Present \\
    \textit{Study Member} \hfill \textit{NPC, Problem Solving Society}
    \begin{itemize}
        \item Discussed and optimized algorithmic solutions focusing on time complexity, Big-O notation, and Dynamic Programming.
        \item Implemented efficient algorithms in C and Python to solve various challenges on platforms like Baekjoon and LeetCode.
    \end{itemize}
\end{itemize}

%----------SELECTED PROJECTS---------------------------------------------------
\section*{Selected Projects}
\hrule
\vspace{4pt}
\begin{itemize}
    \item
    \textbf{Pathfinding Algorithm Visualizer} \hfill Sep. 2025 -- Oct. 2025 \\
    \textit{Python Developer (Personal Project)}
    \begin{itemize}
        \item Created an interactive visualizer for graph traversal algorithms including BFS, DFS, and A* Search.
        \item Utilized Python and Pygame library to demonstrate algorithm execution step-by-step on a grid-based maze.
    \end{itemize}
\end{itemize}

%----------HONORS & AWARDS-----------------------------------------------------
\section*{Honors \& Awards}
\hrule
\vspace{4pt}
\begin{itemize}
    \item \textbf{TOEIC 850}, Educational Testing Service (ETS) \hfill Jan. 2026
\end{itemize}

%----------EDUCATION-----------------------------------------------------------
\section*{Education}
\hrule
\vspace{4pt}
\begin{itemize}
    \item
    \textbf{Sungkyunkwan University} \hfill Mar. 2025 -- Present \\
    \textit{B.S. in Computer Science and Engineering} \hfill \textit{Suwon, South Korea}
    \begin{itemize}
        \item \textbf{GPA}: 4.0 / 4.5
        \item \textbf{Relevant Coursework}: Data Structures (A+), Discrete Mathematics (A+)
    \end{itemize}
\end{itemize}

\end{document}